Analysis

### 2024-03-20 production/prod_analysis-fix-t5.Rmd
update interacciones aleatorias

# generate analytical sample
df_study1 <- 
  df_study_long_t6_comunas %>%
  select(idencuesta,ola,comuna, ponderador_long_total,just_educ, des_perc, merit_effort, merit_talent,education=educ,quintil1:sexo) %>% 
  na.omit() %>% 
  mutate(ola = as.numeric(ola),
         ola_2=as.numeric(ola)^2,
         sexo=as.factor(sexo),
         edad=as.numeric(edad)
         #pos_id=as.numeric(pos_id)
         )

# Hipotesis
h1b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort"
h2b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*des_perc"
h3b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*merit_talent"
h4b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*merit_effort"
h5b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*edad"
h6b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*sexo"

# A. justification educational inequality
educ1 <- lmer(formula(paste0("just_educ~",h1b,"+(ola+I(ola_2)|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ2 <- lmer(formula(paste0("just_educ~",h2b,"+(ola+I(ola_2)+des_perc|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ3 <- lmer(formula(paste0("just_educ~",h3b,"+(ola+I(ola_2)+merit_talent|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ4 <- lmer(formula(paste0("just_educ~",h4b,"+(ola+I(ola_2)+merit_effort|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ5 <- lmer(formula(paste0("just_educ~",h5b,"+(ola+I(ola_2)+edad|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ6 <- lmer(formula(paste0("just_educ~",h6b,"+(ola+I(ola_2)+sexo|idencuesta)")),data = df_study1, weights = ponderador_long_total)

# table 3: interacciones
omit <- "(education)|(ess)|(quintil1)|(pos_id)"
texreg::htmlreg(list(educ1,educ2,educ3,educ4,educ5,educ6),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. All the models are controlled by educational level, subjective social status, political position, and income quintile",
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave",
                                      "Wave^2",
                                      "Age",
                                      "Gender <br> <i>(Ref. Male)</i>",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: effort",
                                      "Wave^2 * Inequality perception",
                                      "Wave^2 * Merit: talent",
                                      "Wave^2 * Merit: effort",
                                      "Wave^2 * Age",
                                      "Wave^2 * Gender"
                                      ),
                file = "output/tables/table3-interac_pond.html")
          #omit.coef = omit

webshot2::webshot(url ="output/tables/table3-interac_pond.html" ,file ="output/tables/table3-interac-pond.png")

>>>>

# generate analytical sample
df_study1 <- 
  df_study_long_t6_comunas %>%
  select(idencuesta,ola,comuna, ponderador_long_total,just_educ, des_perc, merit_effort, merit_talent,education=educ,quintil1:sexo) %>% 
  na.omit() %>% 
  mutate(ola = as.numeric(ola),
         ola_2=as.numeric(ola)^2,
         sexo=as.factor(sexo)
 #        edad=as.numeric(edad)
         #pos_id=as.numeric(pos_id)
         )

# Hipotesis
h1b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort"
h2b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+des_perc*ola_2"
h3b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*merit_talent"
h4b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+merit_effort*ola_2"
h5b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*pos_id"
h6b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*sexo"
h7b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*quintil1"
h8b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*edad"

# A. justification educational inequality
educ1 <- lmer(formula(paste0("just_educ~",h1b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ2 <- lmer(formula(paste0("just_educ~",h2b,"+(ola+ola_2+des_perc|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ3 <- lmer(formula(paste0("just_educ~",h3b,"+(ola+ola_2+merit_talent|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ4 <- lmer(formula(paste0("just_educ~",h4b,"+(ola+ola_2+merit_effort|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ5 <- lmer(formula(paste0("just_educ~",h5b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ6 <- lmer(formula(paste0("just_educ~",h6b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ7 <- lmer(formula(paste0("just_educ~",h7b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ8 <- lmer(formula(paste0("just_educ~",h8b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)

# table 3: interacciones
omit <- "(education)|(ess)"
texreg::htmlreg(list(educ1,educ2,educ3,educ4,educ5,educ6,educ7,educ8),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. All the models are controlled by educational level, subjective social status, political position, and income quintile",
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave",
                                      "Wave^2", 
                                      "Quintile 2 <br> <i>(Ref. Quintile 1)</i>",
                                      "Quintile 3",
                                      "Quintile 4",
                                      "Quintile 5",
                                      "Quintile NA",
                                      "Age 30-49 <br> <i>(Ref. 18-29)</i>",
                                      "Age 50-64",
                                      "Age 65 o más",
                                      "Gender <br> <i>(Ref. Male)</i>",
                                      "Pol. pos: Center <br> <i>(Ref. Left)</i>",
                                      "Pol. pos: Right",
                                      "Pol. pos: Does not identify",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: effort",
                                      "Wave^2 * Inequality perception",
                                      "Wave^2 * Merit: talent",
                                      "Wave^2 * Merit: effort",
                                      "Wave^2 * Center",
                                      "Wave^2 * Right",
                                      "Wave^2 * Does not identify",
                                      "Wave^2 * gender",
                                      "Wave^2 * Quintile 2",
                                      "Wave^2 * Quintile 3",
                                      "Wave^2 * Quintile 4",
                                      "Wave^2 * Quintile 5",
                                      "Wave^2 * Quintile NA",
                                      "Wave^2 * Age 30-49",
                                      "Wave^2 * Age 50-64",
                                      "Wave^2 * Age 65 or more"
                                      ),
                file = "output/tables/table3-interac_pond.html")
          #omit.coef = omit

webshot2::webshot(url ="output/tables/table3-interac_pond.html" ,file ="output/tables/table3-interac-pond.png")
```

```{r }
fit <- lmer(just_educ ~ ola + ola_2 + (ola + ola_2 | idencuesta), data = df_study1)
df_study1$pred_inter_pend_aleatorio <- predict(fit)

# Predictions that ignore random effects:
df_study1$fitted <- predict(fit, re.form = ~0)

# Plot just fixed effects:
plot<-df_study1 %>% 
  ggplot(aes(y = fitted, x = ola_2)) +
  geom_line() +
  theme_light()

ggsave(plot, file="output/graphs/fixed_effects.png")

predict<-interplot::interplot(m = educ1,var1 = "ola",point = T)
predict_data <- predict$data[c(1, 2, 4, 6, 8), ]
predict_data <- predict_data %>% as.data.frame()
